---
title: "My Lab 8"
author: "Pat Byrne"
date: "11/19/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(car) # Just use for the Type III ANOVA check here
library(janitor)
library(ggbeeswarm)
library(kableExtra)
```


## READ
```{r}
penguins <- read_csv('penguins.csv') %>% 
  clean_names()
```

## count by sex n species
```{r}
penguin.counts <- penguins %>% 
  count(species, sex)
```

## Compare flipper sizes for female penguins across species
```{r}
penguin.f <- penguins %>% 
  filter(sex == 'FEMALE')

# Faceted histograms
ggplot(data = penguin.f, aes(x = flipper_length_mm)) +
  geom_histogram() +
  facet_wrap(~species)

# Faceted QQ plot
ggplot(data = penguin.f, aes(sample = flipper_length_mm)) +
  geom_qq() +
  facet_wrap(~species)
```

## Summary statistics
```{r}
penguin.f.summary <- penguin.f %>% 
  group_by(species) %>% 
  summarize(
    mean_flipper_length = mean(flipper_length_mm),
    sd_flipper_length = sd(flipper_length_mm),
    sample_size = n(),
    se_flipper_length = sd(flipper_length_mm)/sqrt(n()),
    var_flipper_length = var(flipper_length_mm)
  )
```

## Adam Levine's Test
```{r}
# H0: variances equal
leveneTest(flipper_length_mm ~ species, data = penguin.f)
# Conlcusion: retain the null
```

Cool so one way ANOVA is chill

## BEES??

Most common error bars:
- st dev
- st error
- CI

```{r}
ggplot() +
  geom_beeswarm(data = penguin.f, 
                aes(x = species, y = flipper_length_mm),
                size = 1,
                alpha = 0.6,
                color = 'gray60') +
  scale_x_discrete(labels = c('Adelie', 'Chinstrap', 'Gentoo')) +
  geom_point(data = penguin.f.summary, 
             aes(x = species, y = mean_flipper_length),
             color = 'red',
             size = 4) +
  geom_errorbar(data = penguin.f.summary,
                aes(x = species, 
                    ymin = mean_flipper_length - se_flipper_length,
                    ymax = mean_flipper_length + se_flipper_length),
                width = 0.2,
                color = 'red')
```


## one way anova
significant flipper length difference between species??????
```{r}
penguin.aov <- aov(flipper_length_mm ~ species, data = penguin.f)
summary(penguin.aov)
```

H0: all means are the same
HA: @ least two means different

Cool means are different

Which ones different significatnyl 
POST HOC TURKEY

```{r}
TukeyHSD(penguin.aov)
```


LADIES AND GENTLEMEN WE HAVE SIGINIFICANCE ACROSS ALL SPECIES

PRAISE TOM SELEK

## Me make nice proportal table

```{r}
party.relig <- gss_cat %>% 
  filter(partyid %in% c('Strong republican', 'Strong democrat')) %>% 
  filter(relig %in% c('None', 'Catholic')) %>% 
  count(partyid, relig)

partytable <- party.relig %>% 
  pivot_wider(names_from = relig, values_from = n)
```

## Doing what i thought we were doing in the last bit

```{r}
party.relig.props <- partytable %>% 
  adorn_percentages(denominator = 'row') %>% 
  adorn_pct_formatting(digits = 1) %>% 
  adorn_ns(position = 'front')

kable(party.relig.props) %>% 
  kable_styling()
```


Are ploitical and religious affiliation independent from each other?
IS there a significant association between political and religious affiliation?
Is there a significant effect of political association on religious affilication?
Is there a significant difference in religious affiliation between strong reps and dems?

```{r}
#contingency table only w actual counts

chi.counts <- partytable %>% 
  select(-partyid)
```

H0: nothing to see here folks

```{r}
my.party.chi <- chisq.test(chi.counts)
my.party.chi
```

There is a significant difference in religious affiliation (none, Catholic) between strong republicans and strong democrats ($\chi^2$ = ..., p < 0.001 )

or 

There is a significant association between party ID and religious affiliation



